---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gtsummary4mice
<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/jrob95/gtsummary4mice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jrob95/gtsummary4mice/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Additional functions for using `tbl_uvsummary` with `mice::mids` objects.
Based on the `tbl_uvsummary` function from the `gtsummary` package, which can be installed from CRAN

The goal of gtsummary4mice is to allow used of `mice` generating multiply imputed data sets `mids` quickly and easily 

## Installation

You can install the development version of `gtsummary4mice` like so:

``` r
# install.packages("pak")
pak::pak("jrob95/gtsummary4mice")
```

## Example

This how to use the `tbl_uvsummary` with objects generated from `mice::mice`

```{r example}
library(gtsummary4mice)
library(gtsummary)
library(mice)


  # Create a sample dataset with missing values
  set.seed(123)
  data <- data.frame(
    outcome = rbinom(100, 1, 0.5),
    predictor1 = rnorm(100),
    predictor2 = rnorm(100)
  )
  data$predictor2[sample(1:100, 20)] <- NA  # Introduce missing values

  # Create mids object using mice
  imputed_data <- mice::mice(data, m = 5, maxit = 5, seed = 123, printFlag = FALSE)

  # Run tbl_uvregression on mids object
  tbl <- tbl_uvregression(
    imputed_data,
    method = glm,
    y = outcome,
    exponentiate = TRUE
  )

```

